\documentclass{article}
\usepackage{listings,amsmath}

%Listings Settings
\lstset{frame=tb,
language=bash,
aboveskip=3mm,
belowskip=3mm,
showstringspaces=false,
columns=flexible,
basicstyle={\ttfamily}
}

%Custom Commands
\newcommand{\git}{{\texttt{git}}}
\newcommand{\github}{{\texttt{Github}}}
\newcommand{\Python}{{\texttt{Python}}}
\newcommand{\python}{{\texttt{python}}}
\newcommand{\Anaconda}{{\texttt{Anaconda}}}
\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}

\begin{document}

\begin{center}

\vspace*{-2.5cm}
\LARGE
\bf{Homework 2}
\vspace{1cm}

\large{Due: Sept 27, 2016}
\vspace{1cm}

\end{center}

Write python functions to calculate integrals using the (right-biased) Riemann Sum, Trapezoid Rule, Simpson's Rule, Romberg integration, and Gaussian Quadrature.  Use the provided \texttt{gaussxy.py} code to calculate the points and weights for Gaussian Quadrature.  Test your methods using the following integrals:
\begin{align}
& \int_0^{4\pi} x^2 \cos(x) \diff x \label{func1}\\
& \int_0^{100\pi} x^2 \cos(x) \diff x \\
& \int_0^1 \sqrt{x} \diff x 
\end{align}

For each function and method calculate the $L_1$ error (absolute value of the difference between the true value and the numerical approximation) for a number of sample points ($N$).  Using this data, calculate the convergence rate $p$ ($L_1 \propto N^{-p}$) for each method on each integral.

Write a \LaTeX{}  report discussing your results. It should include a short explanation of the algorithms with all relevant formula, convergence plots for each test showing the $L_1$ error versus $N$ for all methods, and a discussion that answers the following questions:
\begin{itemize}
	\item Do your empirical convergence rates match theoretical expectations? If not, what properties of the integral lead to the change in behaviour?
	\item Do the methods behave as expected for both small and large values of $N$?  Make sure to try both very small and very large values of $N$.
	\item At what $N$ do the methods become dominated by rounding error?  Does this agree with theoretical predictions?
	\item For function \eqref{func1}, are the error estimates for Trapezoid Rule and Simpson's Rule correct?
	\item Look in detail at the convergence of Romberg Integration and Gaussian Quadrature. Do they converge as a power law at all? Discuss.
\end{itemize}

Include the report \texttt{.tex} file and all Python files in the repo.  Also include either the \texttt{.pdf} version of the report, or all figures necessary to compile it from the \texttt{.tex} file.

\end{document}
